---
title: 'Class 11: Scraping multiple webpages'
author: "Nick Begany"
date: "2026-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning objectives 

- Enable you to scrape multiple webpages (from the same site), using a `for` loop type approach 

- Enable you to scrape multiple webpages (from the same site), using the [purrr package], which is a functional programming approach.
*Note:* In this process, we will create our own function. 


## Re-examining the bulletin example 


Let us try to expand on the example from last class to include the following:
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/)
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/)
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/)
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)

**COMMENT:** Obviously you can repeat your code few times with changing the URL. This will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY Principle**, which stands for **Don't repeat yourself**.  


```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

courses_df = data.frame() # initializing a container to store stuff in the from the loop 
for (abbrv in dept_abbrv) {
  cat(rep("-", 50), "\n")
  print(abbrv)
  bulletin_url = paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
  
  
  
  # we did this so we can reuse the rest of our code with only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles 
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, description = descs)
  print(df$title[1:2])
  courses_df = rbind(courses_df, df)
}
courses_df
```


## `purrr` approach for the same problem 

This is a functional programming approach, and we will write our own function. In R, we use function called `function` to create a function. As opposed to python, R functions return a single object. 


```{r purrr}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# This function takes an abbrv as an input and returns a data_frame as an output 
scrape_mu_bulletin = function(abbrv) {
  bulletin_url = paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
  
  
  
  # we did this so we can reuse the rest of our code with only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles 
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, description = descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'eco')

# to use functions from purrr, we will use a map_*(), or map2_*(), or pmap_*()
# map uses a function that takes a single input (or you are only changing a single input)
# map2 uses a function that takes two inputs 
# pmap >= 3
# after the _, you put the type of object you are getting back 

# the .x is the vector that we will interate over
# and the .f is the function we use 

courses_df_from_purr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```


## scrape data from the website planecrashinfo

The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it contains a database of plane crashes by year.


```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crah_page = rvest::read_html(crash_url)
```

























